The \project{unRAVE} catalog

### 2016-09-07 article/unrave.tex
Clean up all of the cluster text

After verifying that our stellar labels are comparable with other
high-resolution studies, here we verify that the abundances we find
are consistent with expectations from astrophysics.  One example is stars in
globular clusters, which show anti-correlations in light element abundances 
\citep[e.g.,][and references therein]{Norris_Da_Costa_1995,Carretta_2009}.  In the \rave\
survey, \cite{Anguiano_2015} found 70 stars with positions and radial velocities that are
consistent with being members of globular clusters: 49 stars belonging to NGC~5139 ($\omega$~Centauri), 11 members of the retrograde globular cluster NGC~3201, and 10 members of NGC~362. In addition to these systems, 12 stars thought to belong to NGC~1851 were found in the RAVE data in \cite{Kunder_2014} and 10 stars in NGC~6752 and XX stars in \stub{47~Tuc} were discussed in \citep{Kunder_2016}. For a detailed description of the cluster membership for NGC~5139, NGC~3201, and NGC~362 we refer the reader to \cite{Anguiano_2015}. The membership selection for NGC~1851 can be found in \citep{Kunder_2014} and for NGC~6752 and 47~Tuc can be found in \cite{Kunder_2016}. We note here that we have not re-evaluated cluster membership as that is beyond the scope of the paper, however with the results presented here it is possible to study these systems in further detail.

In the top panel of Figure~\ref{fig:globular-cluster-HRD} we plot the spectroscopic H-R diagram for the members of these globular clusters. For comparison, in the bottom panel of Figure~\ref{fig:globular-cluster-HRD} we show the same as the top panel but for the RAVE DR4. In both panels isochrones, we have also plotted the PARSEC isochrones \citep{	
Bressan_2012} for comparison. The basic properties of the globular cluster used to generate the isochrones were sourced from Table 2 of \cite{Kunder_2016}, \cite{Marin-Franch_2009}, and the 2010 version of the Harris Globular Cluster Catalogue \citep{Harris_1996}.This figure indicates that for some stars in specific clusters clusters, namely NGC3201 and NGC362, are slightly offset from the isochrones most likely because the star's metallicity is significantly higher than the mean cluster metallicity. This could be a result of a combination of the inclusion of stars that are not cluster members but appeared to be consistent with the RAVE DR4 stellar parameters. In the remaining globular clusters the stars are consistent with the isochrones. In the case of NGC5139 ($\omega$ cen), it may be possible to pick out two of the several components that exist within that cluster.

All of these systems (\stub{check if this is the case for the remaining two new GCs added.}) in \cite{Anguiano_2015} are well-studied and exhibit abundance anti-correlations 
in Na--O and Mg--Al \citep{Marino_2011,Carretta_2009,Carretta_2013,Munoz_2013}.  Other correlations are also present 
(e.g., C--N), but those relationships are less relevant for this work because 
we do not measure C and N abundances here.  We note that \emph{none} of these 
globular cluster stars were present in our training set.

We show the detailed abundances for these globular cluster members in
Figure \ref{fig:globular-cluster-abundances}.  For comparison purposes we
have included abundances from the high-resolution studies of \citep{people}.
\stub{What do we find?}

% Assuming we recover these relationships...
Indeed, this demonstrates that our abundance labels can be used to identify
globular cluster members that are now tidally disrupted \citep{Anguiano_2016,Kuzma_2016,Navin_2016},
even for stars with low S/N ratios.

% Some literature notes:
%check if NGC 6571 has anticorrelations present
% See http://iopscience.iop.org/article/10.1088/0004-637X/731/1/64/pdf
% NGC 3201 has Na-O anti-correlation: Carretta et al. (2009)
% NGC 362 has "two discrete groups along the Na-O anti-correlation": https://arxiv.org/abs/1307.4085
% NGC 362 has Mg-Al relationship (low Mg scatter, large Al scatter) --> Carretta (2013)
% NGC 362 has a large metallicity spread in RAVE (Anguiano_2015) but not the case in high-res studies (e.g. https://arxiv.org/abs/1307.4085 has a metallicity spread of 0.05/0.08 dex) may indicate better cluster selection needed and can be done with cannon results.
% NGC 3201 has Mg-Al relationship (http://arxiv.org/pdf/1305.3645.pdf and references therein)

%Mean metallicity of NGC3201 cluster = -0.75 +/- 0.20
%Mean metallicity of NGC362 cluster = -0.92 +/- 0.48
%Mean metallicity of NGC5139 cluster = -0.85 +/- 0.55
%Mean metallicity of NGC6752 cluster = -1.17 +/- 0.30

\subsubsection{Open clusters}
\label{sec:open-cluster-validation}
The RAVE survey has observed several open clusters which can serve as a qualitative sanity check that the stellar parameters match our expectations. These include $\sim$160 stars within the Pleiades (78 stars), the Hyades (26 stars), M67 (30 stars) and IC4651 (13 stars) open clusters. Details on the open cluster membership and selection can be found in \cite{Kunder_2016}. The basic properties of the open cluster were sourced from Table 2 of \cite{Kunder_2016} and from \cite{Kharchenko_2013}.

In Figure~\ref{fig:open-cluster-HRD}, we plot the cannon-derived H-R diagram (top panel) and compare it to the RAVE DR4 H-R diagram (bottom panel) for the stars which are likely members of the open clusters. In all cases, except the Pleiades, the stellar parameters derived from the Cannon are consistent with the expectations from the isochrones. We note that theoretical isochrones struggle to match the observed color-magnitude diagrams of young cluster, such as the Pleiades, and thus there has been an effort to use empirical isochrones for such systems \citep[e.g.][]{Bouy_2015}. Additionally, the improvement in the precision of the stellar parameters in the study compared to RAVE DR4 is illustrated in the top and bottom panels of Figure~\ref{fig:open-cluster-HRD} by comparing the tightness of the main-sequence in and sub-giant branch in these open cluster.

We illustrate the precision in the chemical abundance by quantifying the star-to-star dispersion of  the detailed abundances for these open cluster members in
Figure \ref{fig:open-cluster-abundances}.  The internal cluster abundance dispersion can be used as a gauge of precision because open clusters are thought to be chemically homogenous \citep[e.g.][]{Bovy_2016}. 
\stub{What do we find?}

%Mean metallicity of Hyades cluster = 0.07 +/- 0.09 (26 stars)
%Mean metallicity of IC4651 cluster = 0.15 +/- 0.12 (13 stars)
%Mean metallicity of M67 cluster = -0.02 +/- 0.17 (30 stars)
%Mean metallicity of Pleiades cluster = -0.02 +/- 0.12 (78 stars)

\subsubsection{Diffuse interstellar bands}
\label{sec:dibs-validation}

\stub{Look at residuals between model and data as a function of galactic position. This might be out of scope unless someone volunteers to do it}

@@

\bibitem[Mu{\~n}oz et al.(2013)]{Munoz_2013} Mu{\~n}oz, C., Geisler, D., \& Villanova, S.\ 2013, \mnras, 433, 2006

@@

\begin{figure*}[p]
\includegraphics[width=\textwidth]{figures/HRD_GCs.pdf}
\caption{Top Panel: Cannon-derived $\logg$ as a function of $\teff$ for globular cluster members. The cluster name is indicated in the top left corner. The points are color-coded by the metallicity of the member star. Bottom Panel: RAVE DR4 $\logg$ as a function of $\teff$ for the same clusters in the top panel. The points are color-coded by the metallicity of the member star. In both panels, the black line represent the theoretical expectation of a single stellar population from the Padova isochrone set. \label{fig:globular-cluster-HRD}}
\end{figure*}

\begin{figure*}[p]
\includegraphics[width=\textwidth]{figures/HRD_OCs.pdf}
\caption{Same as Figure~\ref{fig:globular-cluster-HRD} for the open cluster members in the RAVE dataset.  \label{fig:open-cluster-HRD}}
\end{figure*}

>>>>

After verifying that our atmospheric parameters and abundances are comparable with other
high-resolution studies, here we verify that the abundances we find
are consistent with expectations from astrophysics.  One example is globular clusters, 
which show anti-correlations in light element abundances 
\citep[e.g.,][and references therein]{Norris_Da_Costa_1995,Carretta_2009}.  In the \rave\
survey, \cite{Anguiano_2015} identified 70 stars with positions and radial velocities that are
consistent with being members of globular clusters: 49 stars belonging to NGC~5139
($\omega$~Centauri), 11 members of the retrograde globular cluster NGC~3201, and 10 
members of NGC~362. In addition to these systems, 12 stars thought to belong to NGC~1851
were found in the \rave\ data by \cite{Kunder_2014}, and a further 10 stars in NGC~6752.  
We refer the reader to those studies for details regarding the membership selection.

In Figure~\ref{fig:globular-cluster-HRD} we show the effective temperature
$\teff$ and surface gravity $\logg$ for pre-defined members of globular clusters in \rave.
The top panels indicate measurements made in this work, and for comparison purposes we have included
the results from the fourth \rave\ data release.  We show representative \project{PARSEC} isochrones 
\citep{Bressan_2012} in all panels, where the isochrone ages and metallicities are adopted from
\citet{Kunder_2016,Marin-Franch_2009}, and the \citet[][accessed 6 September 2016]{Harris_1996} 
online catalog of globular cluster properties.  The globular cluster with the most number of
\rave\ members is NGC~5139 ($\omega$-Centauri), where we find a significant metallicity spread
consistent with high-resolution studies \citep{Marino_2011,Carretta_2009,Carretta_2013}.  We
find the mean metallicity of prescribed $\omega$-Centauri members to be $[{\rm Fe/H}] = -0.85$.
However, it is clear that the membership criteria could be improved with our
revised metallicities and detailed chemical abundances. 
Indeed, this demonstrates that our abundance labels can be used to identify
globular cluster members that are now tidally disrupted \citep{Anguiano_2016,Kuzma_2016,Navin_2016},
even for stars with low S/N ratios.

\subsubsection{Open clusters}
\label{sec:open-cluster-validation}

The \rave\ survey observed $\sim$160 highly probable members of several open clusters:
78 stars in the Pleiades, 26 in Hyades, 30 stars in the Solar-metallicity cluster
M67 and 13 stars in IC4651. Details on the open cluster membership and selection can 
be found in \cite{Kunder_2016}.  We show the effective temperature $\teff$ and surface
gravity $\logg$ for these stars in Figure \ref{fig:open-cluster-HRD}.  The isochrones
are sourced from \citet{Bressan_2012}, with cluster properties adopted from 
\cite{Kunder_2016} and from \cite{Kharchenko_2013}.  We find good agreement between
our atmospheric parameters (top panels) and the isochrones shown.  The position
of the red clump in IC4651 and M67 are perfectly matched to the isochrone, and the
Hyades main-sequence is in good agreement down to $T_{\rm eff} \approx 4000$~K.

The most pronounced discrepancy is seen in the main-sequence of the Pleiades.
Like \citet{Kordopatis_2013}, we find lower $\logg$ values than what the isochrone
shown predicts.  There are two potential reasons for this discrepancy.  Firstly,
we note that theoretical isochrones often struggle to match the observed
color-magnitude diagrams for some young clusters \citep[e.g., the Pleiades, see][]{Bouy_2015}.
Secondly, the lower $\logg$ values we find near the turn-off for the Pleiades could
be explained if those stars are fast rotators. As seen in Figure \ref{fig:test-set-hrd},
for stars with S/N ratios $>10$~pixel$^{-1}$ or $>25$~pixel$^{-1}$, we find many
stars to sit slightly above the turn-off point.  The \rave\ pipeline identifies
these stars to be fast rotators, consistent with the idea that they are blue
stragglers.  Nevertheless, they are slightly higher from the turnoff point, which
may indicate a tendency for fast-rotating turn-off stars to have systematically
lower $\logg$ values, by $\approx$0.2~dex.

@@

@@

\begin{figure*}[p]
\includegraphics[width=\textwidth]{figures/HRD_GCs.pdf}
\caption{Top panels: Effective temperature $\teff$ and surface gravity $\logg$ from this work for prescribed members of globular clusters from \citet{Anguino_2014,Kunder_2014}. Bottom Panels: The same stars are shown as per the top panels, where $\teff$ and $\logg$ have been sourced from the fourth \rave\ data release. A representative Padova \citep{Bressan_2012} isochrone is shown for each cluster in each panel.
\label{fig:globular-cluster-HRD}}
\end{figure*}

\begin{figure*}[p]
\includegraphics[width=\textwidth]{figures/HRD_OCs.pdf}
\caption{Top panels: Effective temperature $\teff$ and surface gravity $\logg$ from this work for prescribed members of open clusters from \citep{Kunder_2016}.  The same stars are shown for each open cluster in the bottom panels, where the $\teff$ and $\logg$ entries are sourced from the fourth \rave\ data release.\label{fig:open-cluster-HRD}}
\end{figure*}
